The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-04-16 paper/iphas-dr2.tex
spellcheck

A. A. Zijlstra$^{15}$.

@@

$^{14}$Joint ALMA Observatory, Alonso de Córdova 3107, Vitacura 763-0355, Santiago, Chile. \\

@@

Information on the quality of each detection is included 
in a series of additional columns.
We draw attention to three useful flags
which warn about the likely presence of a systematic error:
\begin{enumerate}
\item The \emph{saturated} column is used to flag sources
for which the peak pixel height exceeds 55000 counts,
which is typically the case for stars
brighter than 12-13th magnitude in $r$.
Although the pipeline attempts to extrapolate the brightness of
saturated stars based on the shape of the PSF,
such extrapolation is prone to error,
and shoud be viewed as indicative rather than as precise measurement
(systematic uncertainties as a function of magnitude
will be discussed in \S\ref{sec:uncertainties}).
%and we do not recommend reliance on it.
\item The \emph{deblend} column is used to flag sources 
which partially overlap with a nearby neighbour.
Although the pipeline applies a deblending procedure
to such objects, the procedure is currently applied separately
in each band, and hence the $(r-i)$ and $(r-\ha)$ colours
may be inaccurate if the deblending proceeded differently in each band.
\item The \emph{brightNeighb} column is used to flag sources which are located
within a radius of 5 arcmin from an object brighter than $V=7$ 
according to the Bright Star Catalogue (BSC; Hoffleit et al. 1991), 
or within 10 arcmin if the neighbour is brighter than $V=4$.
These brightest stars are known to cause systematic errors
and spurious detections as a result of stray light 
and diffraction spikes.
\end{enumerate}
In addition to the above, we also created warning flags for internal bookkeeping.
For example, we flagged detections which fell in the strongly vignetted regions of the focal plane,
which were truncated by CCD edges,
or which were otherwise affected by bad pixels in the detector.
No such detections have had to be included in the catalogue, as 
alternative detections were available in essentially all these situations
thanks to the IPHAS field pair strategy. In turn, this has meant
that it has not proved necessary to include these internal warning flags
in the pubished source catalogue.

>>>>

A. A. Zijlstra$^{16}$.

@@

$^{14}$Joint ALMA Observatory, Alonso de C\'ordova 3107, Vitacura 763-0355, Santiago, Chile. \\

@@

Information on the quality of each detection is included 
in a series of additional columns.
We draw attention to three useful flags
which warn about the likely presence of a systematic error:
\begin{enumerate}
\item The \emph{saturated} column is used to flag sources
for which the peak pixel height exceeds 55000 counts,
which is typically the case for stars
brighter than 12-13th magnitude in $r$.
Although the pipeline attempts to extrapolate the brightness of
saturated stars based on the shape of the PSF,
such extrapolation is prone to error,
and should be viewed as indicative rather than as precise measurement
(systematic uncertainties as a function of magnitude
will be discussed in \S\ref{sec:uncertainties}).
%and we do not recommend reliance on it.
\item The \emph{deblend} column is used to flag sources 
which partially overlap with a nearby neighbour.
Although the pipeline applies a deblending procedure
to such objects, the procedure is currently applied separately
in each band, and hence the $(r-i)$ and $(r-\ha)$ colours
may be inaccurate if the deblending proceeded differently in each band.
\item The \emph{brightNeighb} column is used to flag sources which are located
within a radius of 5 arcmin from an object brighter than $V=7$ 
according to the Bright Star Catalogue (BSC; Hoffleit et al. 1991), 
or within 10 arcmin if the neighbour is brighter than $V=4$.
These brightest stars are known to cause systematic errors
and spurious detections as a result of stray light 
and diffraction spikes.
\end{enumerate}
In addition to the above, we also created warning flags for internal bookkeeping.
For example, we flagged detections which fell in the strongly vignetted regions of the focal plane,
which were truncated by CCD edges,
or which were otherwise affected by bad pixels in the detector.
No such detections have had to be included in the catalogue, as 
alternative detections were available in essentially all these situations
thanks to the IPHAS field pair strategy. In turn, this has meant
that it has not proved necessary to include these internal warning flags
in the published source catalogue.
